---
title: "BuildingMotif"
---

## Load Tables

We need the licensed version of Netica for this exercise.

```{r}
#| echo: true
#| include: false
#| context: setup
library(PNetica)
library(Peanut)
sess <- RNetica::NeticaSession(LicenseKey=Sys.getenv("NETICA_LICENSE_KEY")) # Add the license key here
RNetica::startSession(sess)
```

Link to the google sheet with the model.

```{r}
#| echo: true
#| include: false
#| context: setup
library(googlesheets4)
googlesheets4::gs4_deauth()
sheetID <- "1oX4ndaEij_dWsap6YR_ZrQYWYUPD6urOsn4vzjBpZIQ"
```

And download the sheets.

```{r Downloads}
netman <- read_sheet(sheetID,"Nets")
nodeman <- read_sheet(sheetID,"Nodes")
omega <- read_sheet(sheetID,"Omega")
QQ <- read_sheet(sheetID,"Q")
stats <- read_sheet(sheetID,"Statistics")
```

## Build Networks

Build the warehouses.

```{r Warehouses}
Nethouse <- PNetica::BNWarehouse(manifest=netman,session=sess,
                                 address=file.path("fullACED"),
                                 key="Name")
Nodehouse <- PNetica::NNWarehouse(manifest=nodeman,
                                  key=c("Model","NodeName"),
                                  session=sess)
```

Process the Omega matrix and build the competency model.  Note, `read_sheet()` returns a tibble, and `Omega2Pnet()` requires a data frame.

```{r ProcessOmega}
CM <- WarehouseSupply(Nethouse,"GeometricOnly")
CM <- Omega2Pnet(as.data.frame(omega),CM,Nodehouse,override=TRUE)
```

Process the Q-matrix and build evidence models.  Again, need to convert tibble to data frame.

```{r ProcessQmatrix}
Qmat2Pnet(as.data.frame(QQ),Nethouse,Nodehouse,override=TRUE)
```
Write out the networks.
```{r}
for (name in netman$Name) {
  if (nchar(name)>0L) {
    net <- WarehouseSave(Nethouse,name)
  }
}
```

## Now build Motif

Get names of items.

```{r}
items <- read.csv("data/allItems.csv")
itemnames <- names(items)[-(1:3)]
```

Need to create mapping from items to evidence models.  Also, need to shorten item names for Netica.

```{r}
emnames <- itemnames
subs <- c("^tC"="c","^tE"="e","^tM"="m","^tR"="r","^tS"="s",
          "^tT"="t","^tV"="v","1[a-f]$"="Easy","2[a-f]$"="Medium",
          "3[a-f]$"="Hard")
for (i in 1:length(subs)) {
  emnames <- sub(names(subs)[i],subs[i],emnames)
}
nodenames <- itemnames
subs1 <- c("Geometric"="Geo","Verbal"="Verb","Explicit"="Expl",
           "Visual"="Vis","Extend"="Ext","Model"="Mod")
for (i in 1:length(subs1)) {
  nodenames <- sub(names(subs1)[i],subs1[i],nodenames)
}
nodenames <- as.IDname(nodenames)
correspondence <- data.frame(itemnames,nodenames,emnames)
correspondence
```

Create an EM for each item and add it to a copy of the competency model.  Rename the `isCorrect` to be the nodename.

```{r}
if (exists("ACEDmotif") && 
    !is.null(WarehouseFetch(Nethouse,"ACEDmotif"))) {
  WarehouseFree(Nethouse,"ACEDmotif")
}
ACEDmotif <- WarehouseCopy(Nethouse,CM,"ACEDmotif")
for (iem in 1:nrow(correspondence)) {
  em <- WarehouseFetch(Nethouse,correspondence[iem,"emnames"])
  obs <- PnetAdjoin(ACEDmotif,em)
  PnodeName(obs[[1]]) <- correspondence[iem,"nodenames"]
}
names(PnetPnodes(ACEDmotif))
```

```{r}
PnetPathname(ACEDmotif) <- "fullACED/ACEDmotif.dne"
WarehouseSave(Nethouse,ACEDmotif)
```


```{r}
PnetCompile(ACEDmotif)
RNetica::JunctionTreeReport(ACEDmotif)
```
## Change data into a case file

```{r}
onodes <- RNetica::NetworkNodesInSet(ACEDmotif,"onodes")
names(onodes)
```

```{r}
allitemsCas <- "fullACED/allItems.cas"
if (file.exists(allitemsCas)) file.remove(allitemsCas)
for (irow in 1:nrow(items)) {
  for (jnode in 1:nrow(correspondence)) {
    node <- onodes[[correspondence[jnode,"nodenames"]]]
    value <- items[irow,correspondence[jnode,"itemnames"]]
   # print(paste(irow,node,value))
    if (!is.na(value)) {
      PnodeEvidence(node) <- ifelse(value>0,"Yes","No")
    } else {
      PnodeEvidence(node) <- NULL
    }
  }
  WriteFindings(onodes,allitemsCas)
  if ((irow%%10) == 0) print(paste("Row ",irow))
}
```

## Build Statistics

```{r}
stats <- as.data.frame(stats)
statlist <- lapply(1:nrow(stats), \(i) {
  Statistic(stats[i,"Fun"],stats[i,"Node"],stats[i,"Name"])
})
names(statlist) <- stats$Name
```



  


## Scoring Timing Tests

```{r}
fstream <- CaseFileStream(allitemsCas,session=sess)
system.time({
fstream <- ReadFindings(onodes,fstream,"FIRST")
outstats <- lapply(statlist,\(st) calcStat(st,ACEDmotif)) |>
  flattenStats()
while(!is.na(getCaseStreamPos(fstream))) {
 fstream <- ReadFindings(onodes,fstream,"NEXT")
 outstats <- rbind(outstats, {
   lapply(statlist,\(st) calcStat(st,ACEDmotif)) |>
     flattenStats()
   })
}
}) -> score_time
score_time

```


## Parameter Learning Tests

```{r}
if (exists("ACEDmotif") && 
    !is.null(WarehouseFetch(Nethouse,"ACEDmotif"))) {
  WarehouseFree(Nethouse,"ACEDmotif")
}
ACEDmotif <- ReadNetworks("fullACED/ACEDmotif.dne",session=sess)
PnetCompile(ACEDmotif)
system.time(
  fit <- GEMfit(ACEDmotif,allitemsCas,tol=.01)
) -> fit.time
fit
fit.time
```

## Write out results

```{r}
profnodes <- RNetica::NetworkNodesInSet(ACEDmotif,"Proficiencies")
obsnodes <- RNetica::NetworkNodesInSet(ACEDmotif,"Observables")
outOmega <- Pnet2Omega(ACEDmotif,profnodes)
outQ <- Pnet2Qmat(obsnodes,profnodes)
write.csv(outOmega,"outOmega.csv")
write.csv(outQ,"outQ.csv")
```

